Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2019-11-21 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd

Climatically, these drought years included three of the five years between 1950 and 2009 with greatest moisture deficit (PET-PRE) during the peak growing season months of May-August (MJJA), which for this site are when annual tree growth is most sensitive [@helcoski_growing_2019]. Specifically, 1966, 1977, and 1999 had mean MJJA PET-PRE of 83.37, 86.97, and 80 mm mo<sup>-1</sup>, respectively. The years 1964 and 2007 also ranked in the top five driest (PET-PRE =83.87 and 82.13 mm mo<sup>-1</sup>), but were not among the lowest in terms of PDSI and were thus not identified as candidate years for inclusion as top drought years (Table S3). **see comment 32**

@@

Community-level tree growth responses to these droughts were modest, with mean resistance values of 0.86, 0.84, and 0.86 for 1966, 1977, and 1999, respectively (Fig. 1b). All droughts yielded about 5% more trees experiencing negative growth ($Rt$ $\le$ 0.7) as defined by our drought threshold, specifically, 29% in 1966, 32% in 1977, and 27% in 1999. However, some trees exhibited increased growth: ($Rt$ > 1.0): 26% in 1966, 22% in 1977, and 26% in 1999. **see comment 33**

@@

Crown position was generally correlated with $H$, but with substantial variation (Fig. 2d). Crown position was a much poorer predictor of $Rt$ than was $H$ (Table 4), lending little overall support to *H1.2* (Table 1). **see comment 34** When considered alone, $CP$ had a significant response only in the 1966 drought, during which trees with dominant $CP$ had the lowest $Rt$. When considered in conjunction with $H$, $CP$ resulted as a significant predictor only for the 1999 drought, during which suppressed and then intermediate trees had the lowest $Rt$. Crown position was included in almost half of the top models, with mixed results as to how $Rt$ varied with $CP$ (Table 5). Most commonly in these multivariate models, as in the univariate models (Table 4), the resistance of dominant trees was less than that of co-dominant trees but higher that of suppressed trees. Although $CP$ was a useful predictor of $Rt$, it overall had a weak effect relative to that of $H$.

>>>>

Climatically, these drought years included three of the five years between 1950 and 2009 with greatest moisture deficit (PET-PRE) during the peak growing season months of May-August (MJJA), which for this site are when annual tree growth is most sensitive [@helcoski_growing_2019]. Specifically, 1966, 1977, and 1999 had mean MJJA PET-PRE of 83, 87, and 80 mm mo<sup>-1</sup>, respectively. The years 1964 and 2007 also ranked in the top five driest (PET-PRE =84 and 82 mm mo<sup>-1</sup>), but were not among the lowest in terms of PDSI and were thus not identified as candidate years for inclusion as top drought years (Table S3).

@@

Community-level tree growth responses to these droughts were modest, with mean resistance values of 0.86, 0.84, and 0.86 for 1966, 1977, and 1999, respectively (Fig. 1b). All droughts yielded about 5% more trees experiencing negative growth ($Rt$ $\le$ 0.7) as defined by our drought threshold, specifically, 29% in 1966, 32% in 1977, and 27% in 1999. However, some trees exhibited increased growth: ($Rt$ > 1.0): 26% in 1966, 22% in 1977, and 26% in 1999.

@@

Crown position was generally correlated with $H$, but with substantial variation (Fig. 2d). Crown position was a much poorer predictor of $Rt$ than was $H$ (Table 4), lending little overall support to *H1.2* (Table 1). When considered alone, $CP$ had a significant response only in the 1966 drought, during which trees with dominant $CP$ had the lowest $Rt$. When considered in conjunction with $H$, $CP$ resulted as a significant predictor only for the 1999 drought, during which suppressed and then intermediate trees had the lowest $Rt$. Crown position was included in almost half of the top models, with mixed results as to how $Rt$ varied with $CP$ (Table 5). Most commonly in these multivariate models, as in the univariate models (Table 4), the resistance of dominant trees was less than that of co-dominant trees but higher that of suppressed trees. Although $CP$ was a useful predictor of $Rt$, it overall had a weak effect relative to that of $H$.
